At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families - Supporting Information

### 2019-11-25 manuscript/reply_to_referees_2.tex

\begin{document}

\begin{letter}{\bf Dr. Jana Vamosi\\
               Editor\\
               Proceedings of the Royal Society B\\
               6-9 Carlton House Terrace\\
               London, UK\\
               SW1Y 5AG\\
                }

\opening{Dear Dr. Vamosi:}

Given the difference of opinion between Referees 1, 3, and 4 and Referee 2, we have prioritised adjusting the manuscript according to the majority view. Nevertheless, we have taken care to address each of Referee 2's comments and, where possible, have used them to improve the manuscript.

@@

	\smallskip

	In what follows we share with authors our specific comments expecting that they will help to re-think the manuscript and get a stronger contribution.

	\end{refquote}

	The Referee(s?) seems to view our basic question and analyses positively, but is rather bluntly critical of our writing in terms of logical, clarity, and style. Some of these criticisms seem to reflect a rather hasty reading of the manuscript, as there are points where the Referee asks why we did not conduct analyses that we did in fact perform or demands that we address biological complications that already appear later in the text. In these cases, we point to existing evidence in the manuscript and have tried to make these connections more obvious. We address the Referee's other comments in detail below (preceded by \textbf{R:}). We hope that this response will clarify the focus and scope of our analyses.

	1. General criticism of the language of the text [[done]]

@@

		\begin{refquote}

		Finally, the text needs English revision by the authors as we feel that some ideas are not clearly stated because of the way they are presented to readers.

		\end{refquote}

		\textbf{R:} As Referees 1 and 3 note, our English is scrupulously correct. Of course technical correctness does not necessarily imply clarity of expression, and we apologise if our choice of vocabulary has obfuscated some of the finer points of the manuscript. We have endeavoured to clarify the manuscript as the Referee suggests.

	2. Title lacks clarity [[fuck off]]

@@

		\begin{refquote}
		Specific comments
		Title
		Your title still lacks clarity and does not reflect the main message you state at the beginning of your discussion (in the first sentence of it you state that you found broad support for the hypothesis that more closely related plants tend to have more niche overlap). We feel that this reflects lack of logical consistency across your manuscript, so re-thinking it should help to define your title.
		\end{refquote}

		\textbf{R:} We have revised the title following a more detailed suggestion by Referee 3 and hope that the new title does not suggest logical inconsistency to this Referee.

@@

		\begin{quotation}

		  Here we investigate how overlap in interaction partners between 
		  pairs of plants (henceforth ``niche overlap'') varies over 
		  phylogenetic distance and how this differs between plant families. 
		  Whereas previous 
		  studies have focused on the presence or absence of phylogenetic
		  signal across entire networks, we take a pairwise perspective in
		  order to obtain a more detailed picture of how plant phylogeny
		  relates to network structure. As different plant families may have experienced different degrees of coevolution, convergence, etc., we also complement analyses with entire networks with comparisons among plants in the same family within a network. 
		  This novel perspective allows us to investigate the relationship between phylogenetic distance and partner overlap at different scales.

  		\end{quotation}

	18. Critique of manuscript structure [[too vague - can't address]]

@@

		\begin{refquote}
			Results
			General: Please, do not include discussion in your results, it may confound readers.
		\end{refquote}

		\textbf{R:} Without knowing where, specifically, the Referee feels that we have included discussion in our results there is little we can do to address this complaint.

@@

	27. Debate over the meaning of "broad"

		\begin{refquote}
			338-339. You state We found broad support for the hypothesis that more closely-related pairs of plants have a higher degree of niche overlap. This is a very strong sentence that is not supported by your results. You found evidence in 55% of plant-pollination networks (almost half of your dataset). In fact, it is interesting to note that even the slope is more pronounced in mutualistic networks you found higher support in herbivory networks, as a higher percentage of networks showed a tendency.
		\end{refquote}

		\textbf{R:}

	28. Confusing complaint about subsetting herbivory networks or perhaps objection to the claim that oligotrophy is common [[done]]

@@

		\begin{refquote}
			351-352 The herbivory networks did not contain as many obligate specialists, but we note that many herbivorous insects are oligotrophs which consume only a few closely-related hosts (Novotny & Basset, 2005; Yguel et al., 2011). This sentence is confuse because you have a subsample of herbivory networks and then this seems to be a by-product of your study design associated with your decision of removing networks that may show strong phylogenetic signal.
		\end{refquote}

		\textbf{R:} We must again point out that subsetting the herbivory networks as we have done was requested during an earlier round of review. We are therefore reluctant to reconsider this approach without a very good reason. Beyond that, it is very difficult to work out exactly what the Referee objects to in this sentence. If the Referee is objecting to our references, note that~\citet{Novotny2005} addresses leaf-chewers as intermediate in their level of specialisation on particular families and emphasises that herbivores in general (regardless of guild) tend to consume a few closely-related hosts. They point out the relative rarity of strict specialists compared to specialists on species within a particular genus or family.~\citet{Brandle2006} also found insect herbivores were specialised on a particular genus but consumed multiple species within the genus. As~\citet{Brandle2006} focus on phytophagous insects specifically, we feel that this reference addresses our point more directly than~\citet{Yguel2011}. We have therefore replaced this reference.

		If the Referee objects to our finding that the herbivores in our networks tended to consume more than one plant species, there is little we can do about it. That is simply what our data say. We do not feel that it is appropriate to look for explanations in the trends we observe in our networks in other types of networks.

		If the Referee is contending that, because of the multiple herbivore types in~\citet{Novotny2005}, we cannot claim that the herbivores in our dataset are oligotrophs, we can respond with further details. The mean number of plants consumed per herbivore ranged between 1.64 and 14.9 across networks, with a mean of 6.36. We hope that the Referee will agree that these low mean degrees do suggest that many of the herbivores in our dataset indeed consume only a few plant species. Our point therefore stands.

@@

	1. Title is confusing

		\begin{refquote}
			Title is confusing – difficult to pick out key message. And given that your analyses broadly give support for effects of phylogenetic distance on niche overlap, why not focus on this message, rather than variability at among individual networks/plant families
		\end{refquote}

		\textbf{R:}

"At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families.”

- suggests that we focus on broad support. Maybe "Broad conservation of pollinators and herbivores in a global dataset"?
"Despite variation among families, pollinators and herbivores are broadly conserved among related plants"?
"Related plants tend to share pollinators and herbivores, but strength of conservation varies among plant families"?

@@

	\textbf{R:} We agree that phylogenetic diversity would be another option for quantifying the 'size' of these networks. However, defining the phylogenetic diversity of each network would depend strongly upon the correctness of of base tree. As we discuss in the methods, our estimates for non-angiosperms are likely to be fairly rough, and some other species are also only approximately dated. Because of this, and because this analysis would more compliment our community-composition analysis than introduce new material, we have opted no to pursue phylogenetic diversity in this manuscript. Here, we were more concerned with numbers of plant pairs since numbers of species are known to affect many areas of network structure. This did not appear to be a major issue for our analyses.

6. Request for consideration of multiple testing [[done]]

	\begin{refquote}
		* Testing within-family existence of a phylogenetic signal
		Examining the strength of phylogenetic signal within plant families is an interesting idea. However, this leads to multiple testing which is prone to type I errors and I could not find mention of correction for this multiple testing in the text. There are actually high chances that there is at least one significant test in each table (1 – (1 – alpha)^N = 0.36 and 0.91 respectively, alpha = 0.05). Yet, the authors can indicate that there are low chances to have that many significant phylogenetic signals (using the probability mass function of the Binomial distribution, see Moran 2003 in Oikos).
	\end{refquote}

	\textbf{R:} The Referee makes a very good point. We had considered these high numbers of significant slopes unlikely to occur by chance, even if we would expect one or two significant results by chance. This argument is somewhat difficult to make convincingly and briefly in the middle of the manuscript, however. Instead, we apply the sequential correlated Bonferroni test in~\citet{Drezner2016}. This development of this test was heavily motivated by the Moran paper you recommend, and we thank the Referee for pointing out this literature. We have added tables of the SCBT critical values to Supplemental Information 4 in order to provide readers with a bit more detail.

	Lines XX-XX now read:

	\begin{quotation}
		 In pollination networks, overlap decreased significantly with increasing phylogenetic distance in 14 of the 48 well-represented families (Table~\ref{family_slopes_pp}; Fig.~\ref{within_family_regression}). If we apply the correlated Bonferroni correction to account for multiple testing~\citep{Drezner2016}, all of these slopes remain significant (\emph{Supplemental Information 4}).
	\end{quotation}

	In responding to this comment, we also noted that the number of significant families in the pollination networks was incorrectly quoted in the main text. As shown in Table 1, there are actually 14 significant families in the pollination web. We have corrected this error and thank the Referee again for calling our attention to this section of the results.

### 2019-11-25 manuscript/phylogenetic_signal_manuscript.tex
more changes. Making progress.

    Considering each family separately, the relationship between within-family niche overlap and phylogenetic distance varied widely in both pollination and herbivory networks. 
    In pollination networks, overlap decreased significantly with increasing phylogenetic distance in 12 of the 48 well-represented families (Table~\ref{family_slopes_pp}; Fig.~\ref{within_family_regression}).
    There was no significant relationship between overlap and phylogenetic distance in
    a further 34 plant families (see \emph{Supporting information 4} for further 
    details). Finally, the overlap between pairs of \emph{Apiaceae} and \emph{Poaceae} increased significantly with increasing phylogenetic distance.

    Of the nine plant families that were sufficiently well represented in herbivory 
    networks, overlap decreased significantly with increasing phylogenetic distance in four 
    (Table~\ref{family_slopes_ph}; Fig.~\ref{within_family_regression}). Four
    families did not show significant relationships between phylogenetic distance and overlap,
    and in one family, \emph{Fabaceae}, overlap of interaction partners increased significantly with 
    increasing phylogenetic distance.

@@

  We found broad support for the hypothesis that more
  closely-related pairs of plants have a higher degree
  of niche overlap. Using a novel method which considers
  all pairs of plants together, 
  the probability of two plants sharing the same animal 
  interaction partners generally decreased with increasing 
  phylogenetic distance. Considering networks separately,
  $\approx$56\%  of the pollination and $\approx$64\% of the 
  herbivory networks exhibited the expected trend of decreasing 
  overlap with increasing distance. This variation between networks
  echoes earlier studies \citep[e.g.,][]{Fontaine2015,Hutchinson2017},
  which also found broad evidence for phylogenetic conservation 
  of interaction partners despite variation between particular 
  networks. The lack of a significant relationship between
  phylogenetic distance and interaction partner overlap in many
  networks could be partly due to the large number of extreme
  specialists, especially among the pollination networks.
  These species interact with only one plant and
  therefore weaken any signal of interaction partner overlap.
  The herbivory networks did not contain as many obligate 
  specialists, but we note that many herbivorous insects are
  oligotrophs which consume only a few closely-related 
  hosts~\citep{Novotny2005,Yguel2011}.
  These oligotrophs may affect overall phylogenetic signal in the same
  way as the specialist partners: in both cases plants in different
  families are unlikely to share interaction partners.

>>>>

    Considering each family separately, the relationship between within-family niche overlap and phylogenetic distance varied widely in both pollination and herbivory networks. 
    In pollination networks, overlap decreased significantly with increasing phylogenetic distance in 14 of the 48 well-represented families (Table~\ref{family_slopes_pp}; Fig.~\ref{within_family_regression}). If we apply the correlated Bonferroni correction to account for multiple testing~\citep{Drezner2016}, all of these slopes remain significant (\emph{Supplemental Information 4}).
    There was no significant relationship between overlap and phylogenetic distance in
    a further 34 plant families (see \emph{Supporting information 4} for further 
    details). Finally, the overlap between pairs of \emph{Apiaceae} and \emph{Poaceae} increased significantly with increasing phylogenetic distance.

    Of the nine plant families that were sufficiently well represented in herbivory 
    networks, overlap decreased significantly with increasing phylogenetic distance in four 
    (Table~\ref{family_slopes_ph}; Fig.~\ref{within_family_regression}). Four
    families did not show significant relationships between phylogenetic distance and overlap,
    and in one family, \emph{Fabaceae}, overlap of interaction partners increased significantly with 
    increasing phylogenetic distance. If we again apply the correlated Bonferroni correction, all five significant slopes remain significant  (\emph{Supplemental Information 4}).

@@

  We found broad support for the hypothesis that more
  closely-related pairs of plants have a higher degree
  of niche overlap. Using a novel method which considers
  all pairs of plants together, 
  the probability of two plants sharing the same animal 
  interaction partners generally decreased with increasing 
  phylogenetic distance. Considering networks separately,
  $\approx$56\%  of the pollination and $\approx$64\% of the 
  herbivory networks exhibited the expected trend of decreasing 
  overlap with increasing distance. This variation between networks
  echoes earlier studies \citep[e.g.,][]{Fontaine2015,Hutchinson2017},
  which also found broad evidence for phylogenetic conservation 
  of interaction partners despite variation between particular 
  networks. The lack of a significant relationship between
  phylogenetic distance and interaction partner overlap in many
  networks could be partly due to the large number of extreme
  specialists, especially among the pollination networks.
  These species interact with only one plant and
  therefore weaken any signal of interaction partner overlap.
  The herbivory networks did not contain as many obligate 
  specialists, but we note that many herbivorous insects are
  oligotrophs which consume only a few closely-related 
  hosts~\citep{Novotny2005,Brandle2006}.
  These oligotrophs may affect overall phylogenetic signal in the same
  way as the specialist partners: in both cases plants in different
  families are unlikely to share interaction partners.

### 2019-11-25 manuscript/supporting_info.tex
more changes. Making progress.

>>>>

    To account for multiple testing, we compared the $p$-values of the significant slopes to critical values in a sequential correlated Bonferroni test~\citep{Drezner2016}. This test accounts for the increased likelihood of obtaining at least one significant result by chance when conducting multiple hypothesis tests, but is less conservative and less prone to type II errors than the original Bonferroni test. All $p$-values remained signficant after applying this test (Table~\ref{SCBT_values}).

    \begin{table}[h!]
        \caption{
          Below, we show the ranked $p$-values for the significant slopes in pollination and herbivory networks side-by-side with the critical values from the SCBT. Any $p$-value which is less than the corresponding critical value remains significant. We obtained critical values separately for the pollination and herbivory networks. }
          \label{SCBT_values}
        \begin{tabular}{l | l | l l |}
        Family & Network type & $p$-value & Critical value \\
        \hline
        \emph{Apocynaceae}      &   pollination &   0.037   &   0.05000 \\
        \emph{Rubiaceae}  &   pollination &   0.026   &   0.03952 \\
        \emph{Amaryllidaceae}   &   pollination &   0.015   &   0.03656 \\
        \emph{Apiaceae}     &   pollination &   0.006   &   0.03300 \\
        \emph{Poaceae}    &   pollination &   0.003   &   0.03009 \\
        \emph{Asteraceae}      &   pollination &   \textless0.001   &   0.02784 \\
        \emph{Boraginaceae}     &   pollination &   \textless0.001   &   0.02610 \\
        \emph{Cistaceae}    &   pollination &   \textless0.001   &   0.02473 \\
        \emph{Fabaceae}    &   pollination &   \textless0.001   &   0.02363 \\
        \emph{Lamiaceae}    &   pollination &   \textless0.001   &   0.02273 \\
        \emph{Lauraceae}    &   pollination &   \textless0.001   &   0.02198 \\
        \emph{Plantaginaceae}  &   pollination &   \textless0.001   &   0.02134 \\
        \emph{Polygonaceae}    &   pollination &   \textless0.001   &   0.02080 \\
        \emph{Ranunculaceae}   &   pollination &   \textless0.001   &   0.02033 \\
        \hline
        \emph{Moraceae}         &herbivory&  0.046 & 0.05000 \\
        \emph{Nothofagaceae}    &herbivory&  0.022 & 0.03201 \\
        \emph{Pinaceae}         &herbivory&  0.020 & 0.02627 \\
        \emph{Poaceae}          &herbivory&  0.006 & 0.02231 \\
        \emph{Rubiaceae}        &herbivory&  \textless0.001 & 0.01952 \\
        \hline
     \end{tabular}
    \end{table}
